\documentclass[a4paper]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{multicol}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{setspace}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{ragged2e}

\usepackage{etoolbox}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-3pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
      {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubheadingc}[8]{
  \noindent
  \begin{minipage}[c]{0.62\linewidth}
    \vspace{-1pt}\item
    \begin{tabular*}{0.3\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
  \end{minipage}\begin{minipage}[c]{0.3\linewidth}
    \vspace{-1pt}\item
    \begin{tabular*}{0.3\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#5} & #6 \\
      \textit{\small#7} & \textit{\small #8} \\
    \end{tabular*}\vspace{-5pt}\end{minipage}
}

\newcommand{\resumeSubheadingb}[6]{
  \vspace{-1pt}\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \vspace{-3pt}
    \textbf{#1} & #2 \\
    \textit{\scriptsize(#3)} & \textit{\scriptsize #4} \\
    \textit{\small#5} & \textit{\small #6} \\
  \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingPro}[2]{
  \vspace{-1pt}\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    #1 & {\textit {\small{#2}}} \\
  \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingProb}[2]{
  \vspace{-1pt}\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    #1 & {\textit {\small{#2}}} \\
  \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingPOR}[2]{
  \vspace{-1pt}\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{   #1} & #2
  \end{tabular*}
  \vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

%\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,
      label={}]}
    \newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
    \newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
%----------HEADING-----------------
\begin{center}
  \textbf{\Huge \scshape Aryaman Raj} \\ \vspace{1pt}
  \faIcon{envelope}
  \href{mailto:20cs3011@rgipt.ac.in}{\underline{20cs3011@r}g\underline{i}p\underline{t.ac.in}}
  $|$
  \faIcon{phone-square-alt} \small
  \href{tel:+917781877310}{\underline{+91-7781877310}} $|$
  \faIcon {linkedin}
  \href{https://www.linkedin.com/in/aryamanraj/}{\underline{LinkedIn}} $|$
  % \faIcon{link} \href{https://ayushr1.github.io/}{{ayushr1.com}} $|$
  \faIcon{github}
  \href{https://github.com/Aryamanraj}{\underline{GitHub}}
\end{center}
%-----------EDUCATION-----------------
\section{Education}

\resumeSubHeadingListStart
\resumeSubheadingb
{\href{https://rgipt.ac.in//}{{{{Rajiv Gandhi Institute of Petroleum
                Technology}}}} }{Jais, UP}
{\href{https://rgipt.ac.in//}{{{An \textbf{Institution of National Importance}
            along the lines of \textbf{IITs}}}}}{}
{Bachelor of Technology in Computer Science and Engineering; CPI: 8.44*}{Dec
  2020 - Jun 2024}
\singlespace
\resumeSubheading
{Central Board of Secondary Education}{}
{Intermediate, 2020: 92.5\% \& Matriculation, 2018: 93.6\%}{}

\resumeSubHeadingListEnd

%------------------Experience-------
\section{Experience}

\resumeSubHeadingListStart
\resumeSubheadingPro
{{{\textbf{Developer Intern}}}	    $|$
  \href{https://www.lighthouse.storage/}{\emph{Lighthouse.Storage}} {}}{}
\resumeItemListStart
\resumeItemWithoutTitle
{\textbf{Technology Stack:} IPFS, Node.js, Solidity, Transak, UniswapV3.}
\resumeItemWithoutTitle
{Working on the fiat to crypto buying feature for users to buy lighthouse's
  perpetual file storage.}
\resumeItemWithoutTitle
{Working with the Node.js backend and RESTful APIs of Lighthouse.Storage.}
\resumeSubHeadingListEnd
\resumeItemListEnd

\resumeSubHeadingListStart
\resumeSubheadingPro
{{{\textbf{BlockOasis}}}      $|$ \emph{Cartesi: The Blockchain OS} {}}{}
\resumeItemListStart
\resumeItemWithoutTitle
{\textbf{Technology Stack:} Cartesi Rollups, Cartesi Machine, Solidity, IPFS
  with Filecoin on WEB3Storage, IoT sensors.}
\resumeItemWithoutTitle
{Building a PoC of a Smart Water Management System using IoT devices that are
  used for real-time monitoring of the quantity and quality of water in the
  distribution infrastructure.}
\resumeItemWithoutTitle
{Collected data from 20+ IoT devices that are stored on IPFS for analysis of
  water usage and wastage, flood, and drought warnings, and water billing.}
\resumeSubHeadingListEnd
\resumeItemListEnd

\resumeSubHeadingListStart
\resumeSubheadingPro
{\href{}{{\textbf{Backend and Block-end Developer}}}	  $|$ \emph{Hearverse}
  \href{}{}}{}
\resumeItemListStart
\resumeItemWithoutTitle
{\textbf{Technology Stack:} Smart Contracts(Solidity), Nodejs, Reactjs, RESTful
  APIs, Postman.}
\resumeItemWithoutTitle
{
  Worked on the Backend API implementation of the Web platform of
  Hearverse.
}
\resumeItemWithoutTitle
{Worked on Smart contract development of Hearverse on Polygon-Mumbai testnet,
  and on a new Layer 1 Blockchain focused on Songs and Music.}

\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------Published Work-----------------
\section{Published Work}
\resumeSubHeadingListStart

\resumeSubheadingPro
{\href{https://github.com/Aryamanraj/ethindiaApi}{{\textbf{Blockchain-based
        Secure Storage and Management of Electronic Health Record}}} \\
{\href{https://github.com/Aryamanraj/ethindiaApi}{{\textbf{using a Smart
        Card}}}} $|$ \emph{Published in IEEE} $|$ \emph{ETHIndia Hackathon 2022} $|$
\href{https://github.com/Aryamanraj/ethindiaApi}{\faIcon{github}} $|$
\href{https://ieeexplore.ieee.org/document/10126943/}{\faIcon{link}}}{Sep 2022}
\resumeItemListStart
\resumeItemWithoutTitle
{\textbf{Technology Stack:} SHA256, Blockchain, Nodejs, Public-Key
  Cryptography, Smart Card, Proof-of-Authority.}
\resumeItemWithoutTitle
{Built PoC of a secure model for the time-stamped storage of EHRs with a
  devised and tested optimized searching algorithm that reduced the searching to
  constant time.}
\resumeItemWithoutTitle
{The Permissioned Blockchain and Lattice Cryptography solved the scalability
  and security issues. The system has been integrated with a smart card.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------Completed proj---------------
\section{Projects}
\resumeSubHeadingListStart
\resumeSubheadingPro
{\href{https://github.com/Aryamanraj/enigma/}{{\textbf{Digital media copyright
          infringement detector}}} $|$ \emph{WON SIH-2022} $|$
  \href{https://github.com/Aryamanraj/enigma}{\faIcon{github}}}{}
\resumeItemListStart
\resumeItemWithoutTitle
{\textbf{Technology Stack:} Solidity, IPFS, WEB3, Etherjs, Nodejs, PUPPETEER
  Library, Expressjs, PyTesseract for OCR.}
\resumeItemWithoutTitle
{Led a team of 6 to design and build a decentralized application on Ethereum
  that identified and flagged websites infringing copyrights on parameters based
  on OCR of images extracted using web scraping tools.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
\resumeSubheadingPro
{\href{https://github.com/Aryamanraj/musicNFTReactApp}{{\textbf{NFT Music
          Application}}} $|$
  \href{https://github.com/Aryamanraj/musicNFTReactApp/}{\faIcon{github}}}{}
\resumeItemListStart
\resumeItemWithoutTitle
{\textbf{Technology Stack:} Reactjs, ERC721, IPFS, Infura.io.}
\resumeItemWithoutTitle
{Deployed a Reactjs-based application with an IPFS database using Infura.io to
  make a profile for the user.}
\resumeItemWithoutTitle
{Implemented ERC721 NFT on the metadata of Songs/Albums uploaded by the user.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Skills}
\resumeSubHeadingListStart
\resumeSubItem{Languages}{C/C++, Python, JavaScript, Typescript, Bash,
  Solidity, HTML5, CSS3, MySQL}
\resumeSubItem{Libraries/Widgets}{WEB3Storage, Selenium, JSEncrypt, OpenSSL,
  GraphQL, Nodejs, Vercel, Nextjs, Hardhat, UniswapV3}
%\resumeSubItem{Areas of Interest}{Blockchain Technology, Data Structures, and Algorithms, Linux, WEB3, IPFS, Cryptography, Ethereum Development, Pentesting, NFTs, ERC-20, ERC-721, ERC-1155, ERC-4337, REST APIs.}
\resumeSubItem{Tools}{Git/GitHub, Docker, Blender, Adobe Illustrator, Adobe
  After Effects, Adobe Photoshop, Adobe Premiere Pro}
\resumeSubHeadingListEnd

%-----------Awards-----------------
\section{Achievements}
\resumeSubHeadingListStart
\resumeSubheadingPro
{\href{}{{\textbf{Received Cartesi Community Grant}}}	  $|$ \emph{Theme: IoT
    \& Blockchain}}{}
\resumeSubheadingPro
{\href{https://github.com/Aryamanraj/enigma/}{{\textbf{WINNER of the Smart
          India Hackathon 2022}}}     $|$ \emph{Theme: Cyber-Security \& Blockchain} $|$
  \href{https://github.com/Aryamanraj/enigma/}{\faIcon{github}}}{}
\resumeSubheadingPro
{ \href{https://github.com/Aryamanraj/uia}{{\textbf{Finalist of UNESCO
          India-Africa Hackathon}}} $|$ \emph{Theme: Drinking Water and Sanitation} $|$
  \href{https://github.com/Aryamanraj/uia}{\faIcon{github}}}{}
\resumeSubheadingPro
{ \href{https://github.com/Aryamanraj/ethindiaApi}{\textbf{Finalist in EthIndia
      Hackathon}} $|$  \emph{Theme: Blockchain in Heathcare} $|$
  \href{https://github.com/Aryamanraj/ethindiaApi}{{\faIcon{github}}}}{}
\resumeSubheadingPro
{{\textbf{Shortlisted \& Granted Scholarship in ETHDenver Hackathon 2023}}
  \emph{} {\underline{\textbf{}}}}{}
\resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Other Activities}
\resumeSubHeadingListStart
\resumeSubItem{OWASP RGIPT Student Chapter}{Founder \&	Lead $|$ \emph{Leading
    a team of 60}}
\resumeSubItem{T\&P Committee, RGIPT}{Training and Placement Coordinator of
  Dept. of CSE}
\resumeSubItem{COSMOSx}{Organized the first three-day International
  Inter-Departmental Technical Fest themed COSMOSx organized by RGIPT ACM Student
  Chapter.}
\resumeSubItem{Gyanarpan, Project Amethi}{Teaching Volunteer \& Organizing Head
  of Gyanarpan, Project Amethi that aims at teaching underprivileged students of
  Amethi district of UP. Leading a group of 150 teaching volunteers.}
\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}